\begin{thebibliography}{99}
\bibitem{g}
    Gonzalez, R. C., \& Woods, R. E. (2010). \emph{Digital Image Processing} 3rd Edition. Pearson Education, Inc.
    
\bibitem{s}
	Leachtenauer, Jon C.  \& Driggers, Ronald. (2000). \emph{Surveillance and Reconnaissance Imaging Systems: Modeling and Performance Prediction}
    
\bibitem{mh}
	Marr, D., \& Hildreth, E. (1980). \emph{Theory of Edge Detection. Proceedings of the Royal Society of London. Series B, Biological Sciences, 207}(1167), 187-217. Retrieved from \url{http://www.jstor.org/stable/35407}

\bibitem{cam}
	Image Sensor Business Division, DSBG. \emph{Sony IMX377CQT Product Summary, Ver. 1.5} Retrieved from \url{http://www.sony-semicon.co.jp/products_en/IS/sensor2/products/imx377.html}
    
\bibitem{hough}
	Hough, P. V. C. (1962). \emph{Methods and Means for Recognizing Complex Patterns} U.S. Patent 3,069,654.
    
\bibitem{lens}
	J. Heikkila \& O. Silven, \emph{A four-step camera calibration procedure with implicit image correction}. Proceedings of IEEE Computer Society Conference on Computer Vision and Pattern Recognition, San Juan, 1997, pp. 1106-1112.
doi: 10.1109/CVPR.1997.609468

\bibitem{ese}
	Ese, E., \emph{Sanntidsprogrammering på samarbeidande mobil-robotar}. Master 2016
    
\bibitem{ese2}
	Ese, E., \emph{Fjernstyring av legorobot}. Prosjekt 2015
    
\bibitem{mw}
	MathWorks. Library of built in functions in Matlab, and their description. \url{https://se.mathworks.com}
    
\bibitem{tor}
	Tøraasen, J. K \emph{Kartlegging ved hjelp av robot og kamerasensor}. Prosjekt 2009
    
\bibitem{image}
	Fisher, R. \emph{Image Processing Learning Resources - Laplacian of Gaussian}. Retrieved from \url{http://homepages.inf.ed.ac.uk/rbf/HIPR2/log.htm}

\bibitem{gsdcalculator}
	Pix4D. \emph{GSD Calculator}. Retrieved from \url{https://support.pix4d.com/hc/en-us/articles/202560249-TOOLS-GSD-Calculator}
    
\bibitem{tesla}
	NVIDIA. \emph{Tesla Motors’ Self-Driving Car “Supercomputer” Powered by NVIDIA DRIVE PX 2 Technology} \url{https://blogs.nvidia.com/blog/2016/10/20/tesla-motors-self-driving/}
    
\bibitem{maker}
The Makers Workbench. \url{http://themakersworkbench.com/}

\bibitem{sos}
HyperPhysics Concepts - Georga State University. \emph{Speed of Sound} \url{http://hyperphysics.phy-astr.gsu.edu/hbase/Sound/souspe.html}
    
\bibitem{rpi}
Raspberry Pi Foundation. \emph{Raspberry Pi 3 Model B} \url{https://www.raspberrypi.org/products/raspberry-pi-3-model-b/}

\bibitem{cam}
Raspberry Pi Foundation. \emph{Raspberry Pi Camera Module} \url{https://www.raspberrypi.org/documentation/hardware/camera/}

\bibitem{canny}
	Canny, J. \emph{"A Computational Approach to Edge Detection,"} in IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. PAMI-8, no. 6, pp. 679-698, Nov. 1986.
doi: 10.1109/TPAMI.1986.4767851

\bibitem{kris}
	Bjørnsen, K. \emph{Mapping a maze with an image sensor}. Prosjekt 2016
    
\bibitem{pi3}
	Element 14 Community \emph{Raspberry Pi 3 Model B Technical Specifications} \url{https://www.element14.com/community/docs/DOC-80899/l/raspberry-pi-3-model-b-technical-specifications}

\end{thebibliography}